Indel Historian: fast and accurate ancestral sequence reconstruction

### 2016-07-23 doc/main.tex
revisions

Multiple alignments are used for several purposes in bioinformatics,
only one of which is homology-directed protein structure prediction,
yet structurally-derived alignments have tended to dominate benchmarks.
Alignment accuracy scores (such as SPS, TCS, AMA, and the Cline shift score) quantify the number of correctly aligned residues
compared to a benchmark dataset of structurally-informed reference alignments \citep{ThompsonEtAl2005}.
Techniques that score highly in these tests include using Bayesian decision theory to maximize the expected
alignment accuracy \citep{NotredameEtAl2000,DoEtAl2005,SchwartzPachter2007,BradleyEtAl2009}
and fine-tuning the alignment scoring function for contextual details, such as the reduced propensity for indels in
hydrophobic protein regions \citep{KatohEtAl2005,Edgar2004b,LarkinEtAl2007}.
These have been accompanied by performance optimizations of 
rate-limiting steps such as all-versus-all pairwise sequence comparison \citep{BradleyEtAl2009,Edgar2004b}.

>>>>

Multiple alignments are used for several purposes in bioinformatics,
only one of which is homology-directed protein structure prediction,
yet structurally-derived alignments have tended to dominate benchmarks.
Alignment accuracy scores (such as SPS, TCS, AMA, and the Cline shift score) quantify the number of correctly aligned residues
compared to a benchmark dataset of structurally-informed reference alignments \citep{ThompsonEtAl2005}.
Techniques that score highly in these tests include using Bayesian decision theory to maximize the expected
alignment accuracy \citep{NotredameEtAl2000,DoEtAl2005,SchwartzPachter2007,BradleyEtAl2009}
and fine-tuning the alignment scoring function for contextual details, such as the reduced propensity for indels in
hydrophobic protein regions \citep{Edgar2004b,KatohEtAl2005,LarkinEtAl2007}.
These have been accompanied by performance optimizations of 
rate-limiting steps such as all-versus-all pairwise sequence comparison \citep{Edgar2004b,BradleyEtAl2009}.
